\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity in Human Brains}

### 2014-01-17 docs/paper/paper final.tex

\begin{figure}[h!]
  \centering
  \includegraphics[height=0.25\textwidth]{images/new/assym_subj1_expl-crop}
  \includegraphics[height=0.25\textwidth]{images/new/assym_subj2_expl-crop}
  \includegraphics[height=0.25\textwidth]{images/new/assym_subj3_expl-crop}
  \includegraphics[height=0.25\textwidth]{images/new/assym_subj4_expl-crop}
  \includegraphics[height=0.25\textwidth]{images/new/assym_subj5_expl-crop}
  \includegraphics[height=0.25\textwidth]{images/new/assym_subj6_expl-crop}
  \caption{The asymetric parts of the partial DAG found with EMS-PC for all six subjects, in which a high value denotes a high certainty of a one-directional arrow.}
\label{fig:asym_subjects}
\end{figure}

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[height=0.26\textheight]{images/new/assym_subj1_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj2_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj3_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj4_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj5_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj6_expl-crop}
  \caption{The assymetric parts of the PDAG found with EMS-PC for all six subjects, in which a high value denotes a high certainty of a one-directional arrow.}
label{fig:asym_subjects}
\end{figure}
